\documentclass[a4paper,11pt]{article}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{lipsum} % For placeholder text



% Commands
\newcommand{\productName}{TrailTrackerUL}

% Page layout
\geometry{margin=1in}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Software Requirements Document}
\fancyhead[C]{TrailTrackerUL}
\fancyhead[R]{\today}
\fancyfoot[C]{\thepage}

% Section title formatting
\titleformat{\section}{\large\bfseries}{}{0em}{} 
\titleformat{\subsection}{\bfseries}{}{0em}{} 

\title{\textbf{Software Requirements Document} \\ \vspace{0.5em} \productName}
\author{Karl Solomon}
\date{}

\begin{document}

\maketitle

\tableofcontents
\vspace{1em}
\hrule
\vspace{1em}

\newpage

\section{Introduction}
This document provides the software requirements for a lightweight and portable GPS tracking device. The purpose of this device is to track the location of assets or individuals in real-time.

\section{Definitions}
\begin{itemize}[label=,itemindent=1em]
	\item \textbf{GPS} - Global Positioning System, a satellite-based navigation system used to determine the location of a device.
	\item \textbf{Session} - A period during which the device records location data for up to 10 days.
	\item \textbf{Real-Time Operating System (RTOS)} - An operating system that manages hardware resources and runs applications with precise timing requirements.
\end{itemize}

\newpage

\section{Functional Requirements}
\begin{enumerate}[label=\textbf{FR\arabic*}, itemindent=1em]
	\item The device shall have an on-off switch.
	\item The device shall have a button to start a new session.
	\item The device shall be able to record at least 10 sessions.
	\item The device shall be able to acquire GPS signals.
	\item The device shall be able to calculate and track the current location.
	\item The device shall be able to record location data for at least 10 days of continuous use.
	\item The device shall have an interface to extract session-data.
\end{enumerate}

\newpage

\section{Non-Functional Requirements}
\begin{enumerate}[label=\textbf{NFR\arabic*},itemindent=2em]
	\item The device shall be lightweight, weighing no more than 100 grams.
	\item The device shall have a battery life of at least 240 hours.
	\item The device shall be able to withstand temperatures from -30°C to 65°C.
	\item The device shall be water-proof.
	\item The device shall be able to withstand a drop of at least 2 meters.
\end{enumerate}

\newpage

\section{System Requirements}
\begin{enumerate}[label=\textbf{SR\arabic*},itemindent=1em]
	\item The device shall run on a real-time operating system.
	\item The device shall have a microcontroller with at least 32-bit architecture.
	\item The device shall record a position at least once per minute.
\end{enumerate}

\end{document}
